Collusion at the 1962 chess world championships

### 2019-04-30 inst/collusion_chess_draws.Rmd
more analysis

>>>>

# Now Curacao

This is the 5th candidates Curacao 1962 results table:

```{r}
jj <- read.table("curacao1962.txt",header=FALSE)
curacao <- as.matrix(jj[,-(1:2)])
players <- as.character(jj$V1)
nationality <- as.character(jj$V2)
rownames(curacao) <- players
colnames(curacao) <- players
curacao[is.na(curacao)] <- ""
curacao <- noquote(curacao)
curacao
```

Now convert to a likelihood function:
```{r}
Hcur <- hyper2(pnames=c("draw","collusion",players))
for(i in seq_len(nrow(curacao)-1)){  # i=row
  for(j in seq(from=i+1,to=ncol(curacao))){ # j = col
    r <- strsplit(curacao[i,j],'')[[1]]
    if((nationality[i]=="USSR") & (nationality[j]=="USSR")){
      monster <- "collusion"
    } else {
      monster <- "draw"
    }
    if(any(r=="W")){  # row player wins
      wins <- sum(r=="W")
      Hcur[  players[i]                    ] %<>% inc(wins)
      Hcur[c(players[i],players[j],monster)] %<>% dec(wins)
    }
    if(any(r=="L")){  # row player loses
      losses <- sum(r=="L")
      Hcur[             players[j]         ] %<>% inc(losses)
      Hcur[c(players[i],players[j],monster)] %<>% dec(losses)
    }
    if(any(r=="W")){  # row player draws
      draws <- sum(r=="D")
      Hcur[                        monster ] %<>% inc(draws)
      Hcur[c(players[i],players[j],monster)] %<>% dec(draws)
    }
  }  # j loop closes
} # i loop closes
Hcur
```

```{r}
dotchart(maxp(Hcur))
```
